Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-08-30 draft/draft0.tex
updates

\subsection{Galaxy angular 2pCF at different redshifts}

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
    \includegraphics[width=18cm]{fig2.eps}
   }
   \caption{\label{fig_diffz}
  2pCF at different redshfits.
   }
\end{figure*}

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
    \includegraphics[width=18cm]{fig3.eps}
   }
   \caption{\label{fig_cosmo}
   2pCF in cosmologies.
   }
\end{figure*}

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig4.eps}
   \includegraphics[width=16cm]{fig5.eps}
   }
   \caption{\label{fig_sys}
  Systematic effects.
   }
\end{figure*}

>>>>

\subsection{Galaxy angular 2pCF: amplitude and shape at different redshifts}

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
    \includegraphics[width=18cm]{fig3.eps}
   }
   \caption{\label{fig_diffz}
  2pCF at different redshfits.
   }
\end{figure*}

The left panel of Figure \ref{fig_diffz} displays the measured angular 2pCF of galaxies (multiplied by scale $r$) in the five snapshot.

The amplitude of 2pCF is crucially affected by the cosmic structure growth and the galaxy bias.
%The amplitude is higher at $z=0$, 
We find $\xi(z=0)>\xi(z=0.5)>\xi(z=1)$.
At low redshift, the large scale structures experienced most gravitational growth,
leading to stronger clustering strength and higher amplitude of 2pCF.
On the contrary, at higher redshift we find $\xi(z=2)>\xi(z=1.5)>\xi(z=1)$,
%The trend is different from $z=1,1.5,2$,
simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

Different from the large variation of amplitude among the different redshifts, %The shape of $r\xi$ also evolves with redshift.
the shape of 2pCF maintains similar at all redshifts. 
At all redshifts, we see the $r\xi$ peaks at $r\sim9 h^{-1}\rm Mpc$,
and monotonically drops at larger or smaller scales.
The only exception is the relative enhancement of 2pCF at $r\lesssim 2 h^{-1}\rm Mpc$,
which is caused by the non-linear growth of structures on small scales 
and becomes more dramatic at lower redshfit.

The middle panel of Figure \ref{fig_diffz} displays the $r\xi$ normalized by the overall amplitude within $5h^{-1}{\rm Mpc} < r < 50h^{-1}{\rm Mpc}$
(here after $\hat r\xi$).
The nice overlapping of the results from five redshifts 
suggests small evolution of shape with redshift.
In the right panel, we compare the high redshift $\hat r\xi$ 
to the $z=0$ result.
There is 1-4\% relative enhancement 
at $r<10h^{-1}\rm Mpc$,
and $<1.5\%$ relative suppression at $r>25 h^{-1}\rm Mpc$.
The trend is monotonic with redshift.

In all, we conclude that the shape of the 2pCF is more robust than the amplitude against redshift and galaxy bias.

\subsection{Galaxy angular 2pCF: in wrong cosmologies }

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
    \includegraphics[width=18cm]{fig4.eps}
   }
   \caption{\label{fig_cosmo}
   2pCF in cosmologies.
   }
\end{figure*}

\begin{figure*}
   \centering{
   \includegraphics[width=16cm]{fig5.eps}
   \includegraphics[width=16cm]{fig6.eps}
   }
   \caption{\label{fig_sys}
  Systematic effects.
   }
\end{figure*}
